\documentclass[12pt]{article}
\setlength{\parindent}{0pt}

\usepackage{geometry}
\geometry{a4paper, margin=1.5in}

\usepackage{times}
\usepackage[letterspace=100]{microtype}
\usepackage[T1]{fontenc}

\usepackage{pagecolor}

\begin{document}
\lsstyle

\definecolor{skyblue}{HTML}{f0f8ff}
\pagecolor{skyblue}

\newcommand{\stub}{\textcolor{skyblue}{\rule{3cm}{3mm}}}

\begin{huge}\begin{center}{\bf kinto behr}\end{center}\end{huge}
\begin{Large}\begin{center}{data scientist}\end{center}\end{Large}
\vspace{1cm}

% Profile ----------------------------------------------------------------------
\begin{large}
{\bf PERSONAL PROFILE} \\
\textcolor{gray}{\rule{2cm}{2mm}}
\end{large}
\vspace{5pt}

\begin{small}
I am a data scientist and statistician with expertise in R and a keen interest in process automation, package development, and applied statistics. Although I am most comfortable in R, I have varying degrees of experience with a number of other languages from SQL (fluent), through Python, HTML/CSS and JavaScript (intermediate), to C++ (beginner). \\

Outside of work, I am an active contributor to the open source software community, having developed or made large contributions to a number of R packages. More information and an expanded resume are available at https://kinto-b.github.io

\end{small}

% Employment -------------------------------------------------------------------
\vspace{1cm}
\begin{large}
{\bf EMPLOYMENT HISTORY} \\
\textcolor{gray}{\rule{2cm}{2mm}}
\end{large}
\vspace{5pt}

{\bf Statistician} \\
\textcolor{gray}{Social Research Centre | 2022 - Present} \\[3pt]
\begin{small}
I am currently situated in the statistical methods team, working on automating our survey weighting procedure for the Life in Australia study.
\end{small}

\vspace{0.5cm}
{\bf Data Scientist} \\
\textcolor{gray}{Social Research Centre | 2020 - 2022} \\[3pt]
\begin{small}
I was the lead data scientist on the SES, which approaches hundreds of thousands of higher education students each year. In this capacity, I was responsible for maintaining the data infrustructure throughout the full length of the pipeline from sample collection and validation through fieldwork operations and data processing, to report production.
\\

In addition, I made key contributions to the in-house R package architecture and Shiny application suite. In particular, I

\begin{itemize}
  \item Authored and/or maintained the majority of in-house packages
  \item Trained other data scientists in R package development, helping them to become maintainers in their own right
  \item Developed a number of complex Shiny applications which became core to projects across the business, including one which won a company-wide competition
\end{itemize}
\end{small}

% Education --------------------------------------------------------------------
\vspace{1cm}
\begin{large}
{\bf EDUCATION} \\
\textcolor{gray}{\rule{2cm}{2mm}}
\end{large}
\vspace{5pt}

{\bf Master of Statistics} \\
\textcolor{gray}{University of New South Wales | 2021 - Present}
\begin{small}
\begin{itemize}
  \item Maintaining a 4.0 GPA with a current rounded average of 90%.
\end{itemize}
\end{small}

\vspace{0.5cm}
{\bf Bachelor of Arts (Honours)} \\
\textcolor{gray}{University of Melbourne | 2021 - Present}
\begin{small}
\begin{itemize}
  \item Graduated top of my class with a GPA of 4.0 and a rounded average of 87\%. (Transcript available upon request).
  \item Wrote a thesis in philosophy on the theory of knowledge.
\end{itemize}
\end{small}

\vspace{0.5cm}
{\bf Bachelor of Arts and Bachelor of Science} \\
\textcolor{gray}{Monash University | 2013 - 2017}
\begin{small}
\begin{itemize}
  \item Achieved a GPA of 3.93 with a rounded average of 87\%. (Transcript available upon request).
  \item Majored in physics and philosophy; minored in mathematics and Japanese language.
  \item Received numerous academic awards including the Dean's List Fellowship Award and five best in unit awards (for achieving top marks across various physics classes).
\end{itemize}
\end{small}

% Other ------------------------------------------------------------------------
\vspace{1cm}
\begin{large}
{\bf SELECTED HONOURS} \\
\textcolor{gray}{\rule{2cm}{2mm}}
\end{large}
\begin{small}
\begin{itemize}
  \item 2019 - Hastie Prize in Philosophy, the University of Melbourne
  \item 2016 - Peter J. Lloyd Prize in Theoretical Physics, Monash University
\end{itemize}
\end{small}

\end{document}
